### 2016-07-06 motivation.tex

Implicit in the above discussion is the assumption of a strongly
consistent ({\sc sc}) store that guarantees the visibility of all
previously committed transactions. {\sc sc} semantics can be built
into the reasoning framework, leading to a proof system tailor-made
for such stores. However, for the reasoning framework to be truly
useful, it has to be parametric over different consistency semantics,
supporting stores that are weaker than {\sc sc} (e.g., causally or
eventually consistent), and should be able to reconcile conflicts
between consistency and isolation constraints.  We demonstrate how our
reasoning framework makes this possible in the following sections.

>>>>

Implicit in the above discussion is the assumption of a strongly
consistent ({\sc sc}) store that guarantees the visibility of all
previously committed transactions. An {\sc sc} semantics can be built
into the reasoning framework, leading to a proof system tailor-made
for such stores.  However, for the reasoning framework to be truly
useful, it should be capable of handling different consistency
semantics, supporting stores that are weaker than {\sc sc} (e.g.,
causally or eventually consistent), and should be able to reconcile
conflicts between consistency and isolation constraints.  We
demonstrate how our reasoning framework makes this possible in the
following sections.

%% We have thus far assumed a strongly consistent ({\sc sc}) store that,
%% in the absence of transactions with special isolation requirements,
%% makes the effects of any operation immediately visible to all
%% subsequent operations. The natural behaviour of {\sc sc} to totally
%% order all operations w.r.t. the $\hbZ$ relation could be in conflict
%% with the constraints imposed by weak isolation. To meet the
%% requirements of weaker isolation levels, say {\sc rc}, the store has
%% to adapt itself to \emph{hide} the effects of concurrent transactions
%% until they are committed. Once committed though, effects need to be
%% immediately visible to subsequent operations. This semantics can be
%% built into the reasoning framework, leading to a proof system
%% tailor-made for such stores. However, for the reasoning framework to
%% be truly useful, it has to be parametric over different consistency
%% semantics, supporting stores that are weaker than {\sc sc} (e.g.,
%% causally or eventually consistent), and should be able to reconcile
%% conflicts between consistency and isolation constraints.  We
%% demonstrate how our reasoning framework makes this possible in the
%% following sections.
